Deterministic Scheduling of Periodic Messages in a Network

### 2017-06-23 article/article.tex
preuve 3nt figure
merge

        We can simplify the weights on the arcs $(s_i,c_s)$ by setting them all to $0$. We order the routes
        in decreasing order of their length, that is when $i<j$, $\lambda(r_{i}) > \lambda(r_{j})$.
        The offset of the route $r_i$ is $i\tau$, which ensures that there are no collision on the way forward (on the arc 
        $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period.        
	We set the waiting time of the first message to $0$, thus it reaches the vertex $c_t$ for the second time before going through the arc $(c_t,c_s)$ at time $2\lambda(r_{0})+\tau$. The process time of the first message is $PT(r_0) = 2\lambda(r_{0})$.
	The second message reaches $c_t$ for the second time at $\tau + 2\lambda(r_{1})$. 
	Therefore to avoid collision, we set the waiting time  $w_1 =  2\lambda(r_{0})+\tau - (\tau + 2\lambda(r_{1})) = 2(\lambda(r_{0}) - \lambda(r_{1}))$.

	We generalize this by setting $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$ for all $i< n$.
	There are no collision on the way back since the message of the route $r_i$ arrives at $c_t$
	at time $(i-1)\tau + 2\lambda(r)$. We must also evaluate the process time. 
	By defintion $PT(r_i) = 2\lambda(r_i) + w_i = 2\lambda(r_i) + 2(\lambda(r_{0}) - \lambda(r_{i})) = 2\lambda(r_0)$.
	Since all process times are the same, the maximum process time is also equal to $2\lambda(r_0)$.

>>>>

        We can simplify the weights on the arcs $(s_i,c_s)$ by setting them all to $0$. We order the routes
        in decreasing order of their length, that is when $i<j$, $\lambda(r_{i}) > \lambda(r_{j})$.
        The offset of the route $r_i$ is $i\tau$, which ensures that there are no collision on the way forward (on the arc 
        $(c_s,c_t)$) as soon as $P \geq n\tau$ which is the minimal possible period.        
	We set the waiting time of the first message to $0$, thus it reaches the vertex $c_t$ for the second time before going through the arc $(c_t,c_s)$ at time $2\lambda(r_{0})+\tau$. The process time of the first message is $PT(r_0) = 2\lambda(r_{0})$.
	The second message reaches $c_t$ for the second time at $\tau + 2\lambda(r_{1})$. 
	Therefore to avoid collision, we set the waiting time  $w_1 =  2\lambda(r_{0})+\tau - (\tau + 2\lambda(r_{1})) = 2(\lambda(r_{0}) - \lambda(r_{1}))$, which is positive since $\lambda(r_{0}) > \lambda(r_{1})$.

	We generalize this by setting $w_i = 2(\lambda(r_{0}) - \lambda(r_{i}))$ which are positive for all $i< n$,
	since by definition.
	There are no collision on the way back since the message of the route $r_i$ arrives at $c_t$
	at time $(i-1)\tau + 2\lambda(r)$. We must also evaluate the process time. 
	By defintion $PT(r_i) = 2\lambda(r_i) + w_i = 2\lambda(r_i) + 2(\lambda(r_{0}) - \lambda(r_{i})) = 2\lambda(r_0)$.
	Since all process times are the same, the maximum process time is also equal to $2\lambda(r_0)$.
